05 - MCMCglmm analyses

### 2021-04-01 Analysis/05-mcmcglmm_analyses.Rmd
Update 05-mcmcglmm_analyses.Rmd

## Procrustes blabla
procrustes <- gpagen(plethspecies$land, print.progress = F)
tree <- plethspecies$phy
```

@@

```{r}
print("ha")
```

>>>>

## Procrustes blabla
procrustes <- gpagen(plethspecies$land, print.progress = F)
tree <- plethspecies$phy
## Making the tree ultrametric
tree$edge.length[which(tree$edge[,2] == 7)] <- tree$edge.length[which(tree$edge[,2] == 7)] + 0.000001
```

@@

```{r, eval = FALSE, print = FALSE}
library(MCMCglmm)
## Running a MCMCglmm model on with all the traits in the PCA
morpho <- as.data.frame(pca$x)
mcmcglmm_data <- data.frame(pca$x, animal = rownames(pca$x))
tree_inverse <- inverseA(tree)$Ainv
priors <- list(R = list(V = 1, nu = 0.002), G = list(G1 = list(V = 1, nu = 0.002)))

phenotype <- pca$x[,1, drop = FALSE]

# simulate phylogenetic and residual effects with unit variance
test.data <- data.frame(phenotype = phenotype, animal = row.names(phenotype))

model1 <- MCMCglmm(fixed = Comp1 ~ 1, random = ~animal, pedigree = tree,
 data = test.data, prior = priors, verbose = TRUE, nitt = 1300, burnin = 300, thin = 1)

test <- MCMCglmm(fixed = cbind(morpho$Comp1, morpho$Comp2) ~ Comp-1, random = ~species, pedigree = tree, prior = priors, data = morpho, verbose = TRUE, nitt = 1300, burnin = 300, thin = 1)

data(bird.families)

phylo.effect <- rbv(bird.families, 1, nodes="TIPS") 
phenotype <- phylo.effect + rnorm(dim(phylo.effect)[1], 0, 1)

plot(model2$VCV)

pca$x ~ pca$x[,1]-1, random = ~
family = c(rep("gaussian"), ncol(pca$x))

formula = 
MCMCglmm::MCMCglmm(fixed = formula, random = mulTree.data$random.terms, pedigree = mulTree.data$phy[[tree]], prior = priors, data = mulTree.data$data, verbose = FALSE, nitt = parameters[1], thin = parameters[2], burnin = parameters[3])

model1.1<-MCMCglmm(cbind(trait1, trait2, trait3, trait4, trait5)  ~ trait-1, random=~us(trait):sire, rcov=~us(trait):units, family=c("gaussian","gaussian","gaussian","gaussian", "gaussian"), prior=prior1, data=data1[[1]], verbose=FALSE, burnin=50000, thin=100, nitt=150000)
